assessment

### 2018-08-27 manuscript/supplementary_notes/metrics/assessment.Rmd
move figures to manual figures
update metrics

```{r}
rule <- dynutils::extract_row_to_list(rules, which(rules$id == assessment$rule_id))
```

\subsection{`r rule$name`}

@@

```{r}
assessment$conformity %>% 
  select(metric_id, conforms) %>% 
  arrange(metric_id) %>% 
  mutate(
    metric_id = label_metrics(metric_id, label_type = "latex") %>% paste0("$", ., "$") %>% forcats::fct_inorder(),
    conforms = kableExtra::cell_spec(
      ifelse(conforms, "\U2714", "\U2716"), 
      background = ifelse(conforms, "#2ECC40", "#FF4136"),
      format = "latex"
    )
  ) %>% 
  spread(metric_id, conforms) %>% 
  knitr::kable(format = "latex", escape = FALSE) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(0, hline_after = FALSE)
```

>>>>

```{r}
rule_ix <- which(rules$id == assessment$rule_id)
rule <- dynutils::extract_row_to_list(rules, rule_ix)
```

## `r rule$name`

@@

```{r}
assessment$conformity %>% 
  select(metric_id, conforms) %>% 
  arrange(metric_id) %>% 
  mutate(
    metric_id = label_metrics(metric_id, format = "latex") %>% as.character() %>% forcats::fct_inorder(),
    conforms = kableExtra::cell_spec(
      ifelse(conforms, "\U2714", "\U2716"), 
      background = ifelse(conforms, "#2ECC40", "#FF4136"),
      format = "latex"
    )
  ) %>% 
  spread(metric_id, conforms) %>% 
  knitr::kable(format = "latex", escape = FALSE) %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::row_spec(0, hline_after = FALSE)
```
